---
title: "Google Play Project Report - CIS 545"
author: "Gabriella Bongiovanni & Syed Shaheryar Qadir"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---
###Google Play Project Report
####This project aims to prescribe a specific price point at which an app should be priced in order to maximize the number of installs.
####Two variables from the dataset will be used in this prescription, Price and Installs.
####Data consists of over 10000 rows and was found on Kaggle.
```{r}
# to install package and call the library
#install.packages("RMySQL")
library(RMySQL)
```
```{r}
# to connec to the database hosted with the login credentials
con = dbConnect(MySQL(),
                user = 'root', password ="",
                dbname = 'googleplaystore', host = 'localhost')
```

```{r}
# to send a query to get all rows from table : 'googleplaystore'
result = dbSendQuery(con,"SELECT*FROM googleplaystore")
```
```{r}
#to establish a data frame with the retrieved result
googledata = fetch(result, n = -1)
#print(googledata)
```

```{r}
#tidy data
library(dplyr)
clean.googledata = googledata %>% select(Category, Rating, Reviews, Installs, Price)

```


####In order to obtain an accurate prescription, first the data will be tidied. The original dataset had several rows in different formats which created difficulties for R to understand the numeric values and instead treated the values as characters rather than numeric.

```{r}
#clean the data 

``` {r}
#to specify value type to each column of the dataset
clean.googledata = na.omit(clean.googledata)

clean.googledata$Category = as.character(clean.googledata$Category)
clean.googledata$Rating = as.numeric(clean.googledata$Rating)
clean.googledata$Reviews = as.integer(clean.googledata$Reviews)
clean.googledata$Installs = as.numeric(clean.googledata$Installs)
clean.googledata$Price = as.numeric(clean.googledata$Price)
print(str(clean.googledata))


```
#Once the data is tidied, it will be randomly split by R to create a testing and training set.
```{r}
# to define the training and the testing set
#install.packages("caTools")
library(caTools)
set.seed(100)
split <- sample.split(clean.googledata$Price,SplitRatio = 0.8)
training_set<- subset(clean.googledata,split==TRUE)
test_set<- subset(clean.googledata,split==FALSE)


```

####To see if a linear model can be used, the correlation between Price and Installs must first be determined. If the correlation is not significant, an alternate method must be used.
```{r}
#see if there is a linear correlation between Price of app and Installs
cor(clean.googledata$Price,clean.googledata$Installs)
```
####According to the function, there is no linear correlation. 
####Below the data can be visualized, and perhaps a trend can be spotted. It is evident from the plot that the highest number of installs happened when the price was lowest. 

```{r}
model <- glm(Installs ~ Price, data = clean.googledata)
```

```{r}
plot(x = clean.googledata$Price, y = clean.googledata$Installs,
   xlab = "price",
    ylab = "installs",
     main = "installs vs price",
   abline(model)
) 
```
####Since the inear model is not signifcant, next a non linear model will be attempted. 
####Below is the code for a non-linear least squares model.
```{r}
m2<-nls(Installs ~ Price*a + b, data = clean.googledata, start = c(a=0,b=0))
```
```{r}
summary(m2)
```
####This model proved much more successful and the p-value is less than 0.05.
####Due to this model's accuracy, it will be used to predict the number of installs if a company was to start selling an app and priced it at a certain point.
```{r}
#set target to obtain prediction
target = data.frame(Price = 0)
result = predict(m2,target)
cat("Number of installs if priced at $0:", result)
```

```{r}
target = data.frame(Price = 0.5)
result = predict(m2,target)
cat("Number of installs if priced at $0.50:", result)
```


```{r}
target = data.frame(Price = 1)
result = predict(m2,target)
cat("Number of installs if priced at $1:", result)
```

```{r}
target = data.frame(Price = 10)
result = predict(m2,target)
cat("Number of installs if priced at $10:", result)
```
####As proven in this predictive model, the higher an app is priced, the number of installs will be negatively affected.
####If a company's goal is to maximize the number installs, the prescribed price according to this model is $0.
